Examining background gene lists in clusterProfiler

### 2023-06-20 example_fixbg.Rmd
look at DAVID data

>>>>

defup <- rownames(subset(def,padj<=0.05 & log2FoldChange>0))
defup <- unique(sapply(strsplit(defup," "),"[[",1))

defdn <- rownames(subset(def,padj<=0.05 & log2FoldChange<0))
defdn <- unique(sapply(strsplit(defdn," "),"[[",1))

bg <- rownames(def)
bg <- unique(sapply(strsplit(bg," "),"[[",1))

# write ensembl IDs for DAVID 
writeLines(text=bg,con="ebg.txt")
writeLines(text=defup,con="eup.txt")
writeLines(text=defdn,con="edn.txt")
